The following is a log/overview of the work done each week.

\subsection{October}\label{october}

\subsubsection{First Week}\label{first-week}

\begin{itemize}
\tightlist
\item
  Researching into competitors and working on the interim report
\end{itemize}

\subsubsection{Second Week}\label{second-week}

\begin{itemize}
\tightlist
\item
  Working on the interim report
\end{itemize}

\subsubsection{Third - Fourth weeks}\label{third---fourth-weeks}

\begin{itemize}
\tightlist
\item
  A majority of time spent working on other projects/modules.
\end{itemize}

\subsection{November}\label{november}

There was a lot of time spent working on other modules due to deadlines.

\subsubsection{First week}\label{first-week-1}

\begin{itemize}
\tightlist
\item
  Working on the interim report and other modules
\item
  03/11/2016 - Exceeded word count and so need to reduce it to below
  2000
\item
  Reading into the Philips Hue API and trying out the app. The API seems
  fairly straight forward, though authenticating with the hub could be a
  challenge.
\item
  There is no need to handle the hub connection through JSON, there is
  instead a Philips hue library that can be imported for use. It
  provides extra functionality to handle all API calls, though I think I
  will opt for directly using the JSON API.
\end{itemize}

\subsubsection{Second Week}\label{second-week-1}

\begin{itemize}
\tightlist
\item
  Worked only on other modules
\end{itemize}

\subsubsection{Third Week}\label{third-week}

\begin{itemize}
\tightlist
\item
  Worked only on other modules
\end{itemize}

\subsubsection{Fourth Week}\label{fourth-week}

\begin{itemize}
\tightlist
\item
  Worked only on other modules
\end{itemize}

\subsection{December}\label{december}

Spent a lot of time working on other projects and being engaged in
family/Xmas events, less work completed than I had hoped.

\subsubsection{First week}\label{first-week-2}

\begin{itemize}
\tightlist
\item
  Working on app, struggled with creating the designs and views.
  Generally getting to grips with the Android SDK
\end{itemize}

\subsubsection{Second Week}\label{second-week-2}

\begin{itemize}
\tightlist
\item
  working on other projects and on app
\end{itemize}

\subsubsection{Third Week}\label{third-week-1}

\begin{itemize}
\tightlist
\item
  No work done
\end{itemize}

\subsubsection{Fourth Week}\label{fourth-week-1}

\begin{itemize}
\tightlist
\item
  Little work done towards other modules
\end{itemize}

\subsection{January}\label{january}

\subsubsection{First week}\label{first-week-3}

\begin{itemize}
\tightlist
\item
  Working on finishing another piece of work due to deadline.
\end{itemize}

\subsubsection{Second Week}\label{second-week-3}

\begin{itemize}
\tightlist
\item
  Worked on application
\end{itemize}

\subsubsection{Third Week}\label{third-week-2}

\begin{itemize}
\tightlist
\item
  Worked on application, a lot of the work towards the
\end{itemize}

\subsubsection{Fourth Week}\label{fourth-week-2}

\begin{itemize}
\tightlist
\item
  02/01/2017 - Attempting to develop the layouts for my app. I'm finding
  a lot of the Android library to be deprecated such as snackbars
  replacing the toast messages; to handle these and correctly show them
  as per the design guidelines is not as straight forward.
\item
  03/01/2017 - Using the container layout with a nested linear/relative
  layout is needed to handle the snackbar and it is now rendering
  correctly. More issues have occurred as I would like a tabbed toolbar
  for navigating through the different aspects of the app such as
  alarm/light control/weather. The tabs require fragments and a
  pageviewer to handle displaying the correct layout and I'm having
  issues with the app closing on start. I have also made an icon for my
  app to replace the default green android.
\item
  04/01/2017 - I am still facing issues with the tablayout as it doesn't
  appear to render correctly and trying to access certain fragments
  closes the app. I'm finding a lot of resources are quite outdated and
  many show incorrect or incomplete implementations.
\item
  05/01/2017 - The tab pages are now working correctly. I have a spinner
  that can display multiple String elements, I am now trying to display
  alarm objects in the list instead but am having difficulties.
\end{itemize}

\subsection{February}\label{february}

\subsubsection{First week}\label{first-week-4}

\begin{itemize}
\tightlist
\item
  Worked on other projects
\end{itemize}

\subsubsection{Second Week}\label{second-week-4}

\begin{itemize}
\tightlist
\item
  Worked on other projects
\end{itemize}

\subsubsection{Third Week}\label{third-week-3}

\begin{itemize}
\tightlist
\item
  Lots of development on the app happened:
\item
  Re-done the tab layout using fragments to avoid using deprecated code.
\end{itemize}

\subsubsection{Fourth Week}\label{fourth-week-3}

\begin{itemize}
\tightlist
\item
  Worked on other projects
\end{itemize}

\subsection{March}\label{march}

This was a heavy month for developing my application

\subsubsection{First week}\label{first-week-5}

\begin{itemize}
\tightlist
\item
  Worked on getting alarms working
\end{itemize}

\subsubsection{Second Week}\label{second-week-5}

\begin{itemize}
\tightlist
\item
  Still working on alarms, using pending intents and broadcast receiver
  is more complicated than expected.
\end{itemize}

\subsubsection{Third Week}\label{third-week-4}

\begin{itemize}
\tightlist
\item
  Include lights, had a bit of trouble getting the bridge connected
  properly
\end{itemize}

\subsubsection{Fourth Week}\label{fourth-week-4}

\begin{itemize}
\tightlist
\item
  Bridge not connecting/showing, there was an error in the logic
  detecting if bridge had been connected.
\item
  Improving lights and alarms.
\item
  Got weather working
\end{itemize}

\subsection{April}\label{april}

This month involved a lot of report writing

\subsubsection{First week}\label{first-week-6}

\begin{itemize}
\tightlist
\item
  Every day of the week spent writing the report
\end{itemize}

\subsubsection{Second Week}\label{second-week-6}

\begin{itemize}
\tightlist
\item
  Every day of the week spent writing the report
\end{itemize}

\subsubsection{Third Week}\label{third-week-5}

\begin{itemize}
\tightlist
\item
  Working on reports for other modules.
\end{itemize}

\subsubsection{Fourth Week}\label{fourth-week-5}

\begin{itemize}
\tightlist
\item
  Less work was done this week, worked on developing app for a different
  module and writing the report for that work instead.
\end{itemize}

\subsection{May}\label{may}

\subsubsection{First week}\label{first-week-7}

\begin{itemize}
\tightlist
\item
  Writing more for the report
\item
  Wrote application documentation
\end{itemize}

\subsubsection{Second Week}\label{second-week-7}

\begin{itemize}
\item
  Proof-read, bound and submitted work.
\item
  --/--/---- - Met with Marcus
\item
  --/--/---- - Met with Marcus
\end{itemize}
