\section{Original Project Plan}\label{original-project-plan}

The following is the original project plan for my application.

\subsection{Aims and objectives}\label{aims-and-objectives}

What I will be developing over the upcoming months is an app to help
users get out of bed easier in the morning in a useful and information
rich way.

My aims are:

\begin{itemize}
\tightlist
\item
  Produce an alarm app with all the functionality users are used to.
\item
  Integrate Smart bulb functionality into the app to turn the light on
  in the morning with the alarm.
\item
  To turn off the lights at night without having to get out of bed.
\item
  Provide weather information for the day.
\item
  Inform the user of their schedule for the day and upcoming events.
\item
  Publish the application to the play store for download and use by
  others.
\end{itemize}

\subsection{Stakeholders}\label{stakeholders}

I have identified the following stakeholders:

\begin{itemize}
\item
  Myself - Not only am I developing the application making me a
  stakeholder, I am also very interested in home automation and waking
  up happy.
\item
  My supervisor, Marcus Winter - By accepting to be my supervisor Marcus
  is also a stakeholder for my application.
\item
  The second reader - Will also be involved and will be grading my
  project.
\item
  An expanding user base of smart bulbs - Although the market currently
  is small the cost of smart bulbs is decreasing making them more
  available to users.
\item
  Anyone that uses an alarm - The largest stakeholder I have is anyone
  that uses an alarm on the Android platform. More specifically those
  who own smart bulbs or other connected devices.
\end{itemize}

\subsection{Communications}\label{communications}

I will maintain contact with my project supervisor with monthly meetings
where I intend to measure my progress against deadlines and goals,
reflect on what progress has been made and address issues, challenges
and for development advice to assist me successfully complete my project
as planned.

Regular emails will also be used between meetings to keep in contact and
keep my supervisor informed of what I intend to talk about and on my
progress made.

\subsection{Installation Process}\label{installation-process}

I would like to publish my application to the Play store once developed
to a satisfactory level. To install an app from the Play store you can
simply select the option to install the app and it will be downloaded
and installed seamlessly.

I will be ensuring to develop to a high standard and ensure there are no
issues, bugs or flaws with my application.

\subsection{Quality checks}\label{quality-checks}

During development I will ensure to maintain my code and follow the
principles that have been taught to me and that I have learned and will
learn, in doing so my code should be easily maintainable, readable and
extendable for possible extensions and stretch goals.

I will develop a test plan as I continue to develop my application to
allow me to note issues and ensure previous functionality has not been
effected by further developments.

\subsection{How will I measure
success?}\label{how-will-i-measure-success}

My key performance indicators are outlined below:

\begin{itemize}
\tightlist
\item
  Alarm functionality
\item
  Smart bulb integration
\item
  Weather functionality
\item
  Calendar Integration (Stretch)
\item
  Text to speech (Stretch)
\end{itemize}

If I am unable to produce a working alarm app with smart bulb
functionality I will have failed to achieve what I intended to develop
and so these are my highest priority.

\subsection{Challenges}\label{challenges}

There are many challenges I will face during my project these include
the following:

\begin{itemize}
\item
  Making my application extensible to other home automation systems such
  as the \cite{belkinwemo}. This would allow for greater flexibility and
  a larger target audience.
\item
  Handling various devices, there are now many various appliances that
  are connected to home automation, from washing machines and fridges to
  door locks and CCTV. Many devices could be useful for morning and
  night automation, such as closing the curtains at night or turning the
  kettle on in the morning. Each of these devices will have different
  functions and are very different from one another. To be able to add
  several and include them within a scene/scenario to perform multiple
  actions would be a very powerful inclusion within the app.
\item
  Providing a good level of home automation without making the app
  cumbersome or difficult to use. My target audience is average users
  who would like to wake up easier and more refreshed and have their
  days information available straight away. They don't want to spend
  ages setting up the light bulbs or struggling to find settings as they
  will get fed up and stop using and potentially uninstall the app.
\end{itemize}

\section{Divergence From Original
Plan}\label{divergence-from-original-plan}

No project goes through all the stages of development and remains
exactly as outlined during the first stages of development. This is
attributed to many factors that may not have been apparent at the onset
of development, many changes are small involving adjustments to the UI
to improve user experience; these changes can be seen in completed
products also, with many applications receiving design overhauls such as
the introduction of the ribbon design to the Microsoft office suite for
office 2007 \parencite{officeribbon} and the regularly changing design
philosophy of Android.

\subsection{User Testing/Evaluation}\label{user-testingevaluation}

Through getting others to use my application I was able to gain useful
feedback to alter the design and functionality of my application to
improve upon the designs.

Due to the need for a hue lighting bridge to be available, it was not
always possible to obtain hands on feedback from users and instead
required the need to obtain feedback through the use of screenshots and
describing the actions available to the user; through this limitation it
was not possible to gain the most feedback possible, but should provide
a good insight into the design and enhancements for the application.

\subsubsection{Inclusion of the Light
Icon}\label{inclusion-of-the-light-icon}

Several users suggested the inclusion of a lighting icon to indicate the
type of light being listed, this is because of the ability for lights to
be renamed and could lead to confusion in the future.

The icon provides at a glance a hint to the type of light being shown
and can assist the user. Within the application the icons used are
freely available and provided by Philips under the development program
to promote development and use of the Hue lighting system
\parencite{hueicons}.

\subsubsection{Greater Control of
Lights}\label{greater-control-of-lights}

Many users suggested a greater level of lighting control within the
application, features such as; the ability to connect with multiple
bridges, add new lights to the system, adjust brightness and colour.
Each of these features could make for a more enjoyable user experience
and allow the users to perform many function from within the
application, however due to complexity in certain aspects such as
allowing for multiple bridges, these were not possible to be included
within the application.

Features such as the brightness and hue controls were not included as a
design limitation, with the belief that adding these features would add
an extra level of complexity of use that was not intended for the
application. During the conceptual phase of development a goal for a
clean and minimal design was set, resulting in simplicity of use.

I would like to include these controls if possible in the future but I
would like to find a user friendly means of providing the controls. Hue
adjustment would be more complex than the inclusion of a brightness
adjustment as brightness can be linearly controlled while the hue
involves; hue, saturation, colour temperature and the use of the CIE
colour space \parencite{1475-4878-30-4-301}. Due to this complexity it
is unlikely to be included within my application in the near future.
